MP MetaAnalysis

### 2018-11-09 Paper_Analyses.Rmd
added histograms for time-related analysis choices

trial.l <- cor.test(dat$trial_length, dat$mean_age_1)
trial.length.plot <- ggplot(dat, aes(trial_length, age.C)) + geom_point() +geom_smooth(method = "lm")

>>>>

trial.l <- cor.test(dat$trial_length, dat$mean_age_1)

library(reshape)
tdl <- dat[,c("short_cite", "trial_length", "post_nam_dur")]
tdl <- melt(tdl, id = "short_cite")

trial_length_hist <- ggplot(dat,aes(x=value)) + 
  apatheme+
    geom_histogram(data=subset(tdl,variable == 'trial_length'),fill = "red", alpha = 0.5) +
    geom_histogram(data=subset(tdl,variable == 'post_nam_dur'),fill = "blue", alpha = 0.5)
